Paper 2, Econ 980x

### 2022-11-28 Paper2.Rmd
commit

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readxl)
library(ggplot2)
library(janitor)
library(ggthemes)
library(stargazer)

@@

stargazer(g, y, a, title="Various Models", align=TRUE)
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readxl)
library(ggplot2)
library(janitor)
library(ggthemes)
library(stargazer)
#library(tinytex)

@@

stargazer(g, y, a, title="Various Models", align=TRUE, type = "text")
```
